---
title: "First Post"
author: "Benjamin Ng"
date: 2018-04-26T21:13:14-05:00
categories: ["Blog"]
tags: ["Personal"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Hello World!

The website is up, and now the posting can begin! Over the course of the next few months, I'll be documenting my journey as I explore and learn about data visualization, spatial analysis, text mining and machine learning (ambitious list, I know).

## Setting up this Blog

For those interested in turning your github page into a similar webpage, I followed the guide provided by Aurora Mareviv [here](https://aurora-mareviv.github.io/talesofr/2017/08/r-blogdown-setup-in-github/). She has an updated guide if you're using project pages on github, but I found that the first guide was more straightforward if you're using your personal github page.

## Mandatory R Content

*Just to make sure my code chunks work*

```{r pressure, echo=FALSE}
summary(cars)
plot(pressure)
```

Till next time!
